---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# journalabbr 

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/journalabbr)](https://CRAN.R-project.org/package=journalabbr)
![r-universe](https://fastverse.r-universe.dev/badges/journalabbr)
[![downloads](http://cranlogs.r-pkg.org/badges/grand-total/journalabbr?color=blue)](https://cran.r-project.org/package=journalabbr)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/last-month/journalabbr?color=blue)](https://github.com/zoushucai/journalabbr)
[![R build status](https://github.com/zoushucai/journalabbr/workflows/R-CMD-check/badge.svg)](https://github.com/zoushucai/journalabbr/actions)
[![Codecov test coverage](https://codecov.io/gh/zoushucai/journalabbr/branch/master/graph/badge.svg)](https://app.codecov.io/gh/zoushucai/journalabbr?branch=main)
[![CRAN status](https://www.r-pkg.org/badges/version/journalabbr)](https://CRAN.R-project.org/package=journalabbr)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![License: GPL](https://img.shields.io/badge/license-GPL-blue.svg)](https://cran.r-project.org/web/licenses/GPL)
<!-- badges: end -->

## Function

Implementing journal abbreviation for the 'Journal' field in BibTex file.

## Install

```{r,eval=FALSE}
# CRAN
install.packages("journalabbr")

# or 
devtools::install_github("zoushucai/journalabbr")
```

## Require

The format of the bib file is as follows:

``` latex
@***{****,
  **** = {****},
  **** = "*****",
  *** = {{******}},
  **** = {*****}}

% or

@***{****,
  **** = {****},
  **** = "*****",
  *** = {{******}},
  **** = {*****}
  }
  
```

Except for the `@`character line, the rest of the field lines must have an equal sign `=`

## Use

```{r}
require(journalabbr)
path0 <- system.file("extdata", "testfile_1.bib", package = "journalabbr", mustWork = TRUE)
temp <- abbr_bib(file = path0, out.file = tempfile(fileext = ".bib"))
colnames(temp)

path <- system.file("extdata", "testfile_2.bib", package = "journalabbr", mustWork = TRUE)
temptab <- abbr_bib(file = path, out.file = tempfile(fileext = ".bib"))
colnames(temptab)

# add user csv
csvpath <- system.file("extdata", "myabbr.csv", package = "journalabbr", mustWork = TRUE)
temptab1 <- abbr_bib(file = path, out.file = tempfile(fileext = ".bib"), user.csv = csvpath)
colnames(temptab1)

# no return value
abbr_bib_only_journal(file = path, out.file = tempfile(fileext = ".bib"), user.csv = csvpath)

```

or run shiny 

```{r,eval=FALSE}
journalabbr::run_example()
```

or run shiny online

website: [https://zoushucai.shinyapps.io/shiny_cankaowenxian/](https://zoushucai.shinyapps.io/shiny_cankaowenxian/)


- It needs to be manually pushed to `shinyapps.io`, and the implementation is also very simple. Simply click the mouse in `Rstudio` to operate it


### Access internal data

```{r}
abbrtable = journalabbr:::abbrtable_sys
colnames(abbrtable)
```

